What are the contributing factors to poor mental health in U.S?

### 2022-03-21 outputs/paper/paper.Rmd
Update paper.Rmd

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('C:/Users/Isfan/Desktop/Supplemental Survey Screen Shots/001.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('C:/Users/Isfan/Desktop/Supplemental Survey Screen Shots/002.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('C:/Users/Isfan/Desktop/Supplemental Survey Screen Shots/003.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('C:/Users/Isfan/Desktop/Supplemental Survey Screen Shots/004.png')
```

>>>>

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/001.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/002.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/003.png')
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('("../../outputs/paper/supplemental survey/004.png')
```
